### 2017-07-13 README.Rmd
update implementation status
add ci for slope

One categorical (2 level) variable

@@

Two categorical (2 level) variables

@@

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ 1
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

@@

>>>>

One categorical (2 level) variable (implemented up to calculate())

@@

Two categorical (2 level) variables (implemented)

@@

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

@@

```
mtcars %>%
  specify(mpg ~ hp) %>% 
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "slope")
```
